---
title       : Creating a Vector
description : In this chapter we will learn how to create a vector


--- type:NormalExercise lang:r xp:50 skills:1 key:0b8961fe9d
##Creating a Vector

In this chapter we will create a vector.

- A vector is a simple tool to store data.
- To create a vector in R, we use the **c()** function aka combine function.
- A vector is of mainly 3 types:
*   a. **Numeric Vector** - one that contains only numeric values (integer of float).
*   b. **Character Vector** - one that contains either single character values or strings as values.
*   c. **Logical Vector** - one that contains logical values (TRUE or FALSE).

- Here are some examples to get you started.

##### Create a numeric vector
```code numeric_vector <- c(1,2,3,4,5)```

##### Create a float vector
```float_vector <- c(10.0,20.0,30.0,40.0,50.0)```

##### Create a character vector with single characters
```scharacter_vector <- c('H','e','l','l','o')```

##### Create a character vector with single characters
```character_vector <- c('Hello','Python','Scala','Java','PHP')```

##### Create a logical vector
```logical_vector <- c(TRUE,FALSE,FALSE,TRUE,FALSE)```


*** =instructions
- create the vectors as taught in information.
- click submit to run.

*** =hint
- click Submit to run the code.

*** =pre_exercise_code
```{r}

```

*** =sample_code
```{r}
# create a numeric_vector with values from 21 to 30

# print the numeric_vector

# create a character_vector with values from A to H

# print the character_vector

# create a logical_vector with values from TRUE,FALSE,FALSE,TRUE,TRUE

# print the logical_vector

```

*** =solution
```{r}
# create a numeric_vector with values from 21 to 30
numeric_vector <- c(21:30)
# print the numeric_vector
print(numeric_vector)

# create a character_vector with values from A to H
character_vector <- c('A','B','C','D','E','F','G','H')
# print the character_vector
print(character_vector)

# create a logical_vector with values from TRUE,FALSE,FALSE,TRUE,TRUE
logical_vector <- c(TRUE,FALSE,FALSE,TRUE,TRUE)
# print the logical_vector
print(logical_vector)
```

*** =sct
```{r}
msg_bad <- "You have got it wrong!!!"
msg_success <- "Good work!!!"
test_mc(correct = 2, feedback_msgs = c(msg_bad, msg_success, msg_bad, msg_bad))

```

--- type:NormalExercise lang:r xp:50 skills:1 key:33331b1823
##Creating a Vector using the : (colon) operator

You can also create create a vector using the **:** operator.
Take a look at the example below:

```
vector_a <- 5:13
```
the output of this will be : 5, 6, 7, 8, 9, 10, 11, 12, 13

The same thing can be done for a float vector

```
vector_b <- 4.5:10.5
```

The output of this will be : 4.5, 5.5, 6.5, 7.5, 8.5, 9.5, 10.5


*** =instructions
- create a vector a using : (colon) operator.
- create a float vector using : operator.
- create a vector in descending order using : operator.

*** =hint
- You have to use : operator. 

*** =pre_exercise_code
```{r}

```

*** =sample_code
```{r}
# create a vector a with values from 15 to 22

# print the vector a

# create a float vector b with values from 2.3 to 6.7

# print the float vector

# create a vector c with values from 10 to 2 in descending order

# print the vector c

```

*** =solution
```{r}
# create a vector a with values from 15 to 22
a <- 15:22
# print the vector a
a
# create a float vector b with values from 2.3 to 6.7
b <- 2.3:6.7
# print the float vector
b
# create a vector c with values from 10 to 2 in descending order
c <- 10:2
# print the vector c
c
```

*** =sct
```{r}
# SCT written with testwhat: https://github.com/datacamp/testwhat/wiki

test_function("str", args = "object",
              not_called_msg = "You didn't use : operator!",
              incorrect_msg = "You didn't use : operator with the correct argument, `object`.")

test_object("c")

test_error()

success_msg("Great work! Keep Going!!!")

```
